---
title: "Final Project"
author: "Caijun Qin"
date: '2022-04-14'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Survival analysis packages.

```{r}
packages.survival <- c("survival", "survminer", "SurvMetrics")
install.packages(packages.survival)
lapply(X = packages.survival, FUN = library, character.only = TRUE)
```

Load data.

```{r}
kickstarter.data <- read.csv(file = "./data/kickstarter_1.csv", header = TRUE)
kickstarter.data <- kickstarter.data  %>% 
  dplyr::mutate_if(.predicate = is.integer, .funs = as.factor) %>% 
  mutate(day_succ = as.integer(x = day_succ), Status = as.integer(x = Status))

kickstarter.data
```

Descriptive statistics of dataset.

```{r}
ncol(x = kickstarter.data)
nrow(x = kickstarter.data)
summary(object = kickstarter.data)
unique(kickstarter.data$day_succ)/
```

Kaplan-Meier as Control.

```{r}
fit <- survival::survfit(formula = survival::Surv(time = day_succ, event = Status) ~ 1, data = kickstarter.data)
fit
plot(x = fit, main = "Kaplan-Meier Plot", xlab = "Days", ylab = "Count of Ongoing Projects")
```

Summary of KM model.

```{r}
# summary of survival curves
fit.summary <- summary(object = fit)

# sort summary table
fit.summary$table
```

Re-organizing KM model summary as dataframe.

```{r}
fit.df <- data.frame(
  time = fit$time,
  n.risk = fit$n.risk,
  n.event = fit$n.event,
  n.censor = fit$n.censor,
  surv = fit$surv,
  upper = fit$upper,
  lower = fit$lower
)
fit.df
```

KM plot considering only time.

```{r}
survminer::ggsurvplot(
          fit = fit,
          pval = TRUE, 
          conf.int = TRUE,
          conf.int.style = "step",
          risk.table = "abs_pct", # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          risk.table.y.text.col = TRUE,# colour risk table text annotations.
          risk.table.y.text = FALSE,
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          
          main = "Kaplan-Meier Plot",
          xlab = "Time (Days)",
          ylab = "Survival Probability",
          
          ggtheme = ggplot2::theme_bw(), # Change ggplot2 theme
          palette = c("#E7B800", "#2E9FDF")
)
```

Kaplan-Meier fitted against all factors (for dataset description).

```{r}
kickstarter.factor.names <- colnames(x = kickstarter.data %>% dplyr::select_if(.predicate = is.factor))
formula.all <- eval(parse(text = paste0("survival::Surv(time = day_succ, event = Status) ~", paste0(kickstarter.factor.names, collapse = ' + '))))
fit.all <- survival::survfit(formula = formula.all, data = kickstarter.data)
saveRDS(object = fit.all, file = "fit.all.rds")
fit.all
plot(x = fit.all, main = "Kaplan-Meier Plot", xlab = "Days", ylab = "Count of Ongoing Projects")
```

KM plot considering only time.

```{r}
fit.reduced <- survival::survfit(formula = survival::Surv(time = day_succ, event = Status) ~ facebook_connected + has_video, data = kickstarter.data)
saveRDS(object = fit.named, file = "fit.named.rds")
survminer::ggsurvplot(
          fit = fit.reduced,
          pval = TRUE,
          conf.int = TRUE,
          # conf.int.style = "step",
          risk.table = "abs_pct", # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          risk.table.y.text.col = TRUE,# colour risk table text annotations.
          risk.table.y.text = FALSE,
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival

          main = "Kaplan-Meier Plot",
          xlab = "Time (Days)",
          ylab = "Survival Probability",
          
          ggtheme = ggplot2::theme_bw(), # Change ggplot2 theme
          legend.labs = rev(x = c("Neither", "Video", "FB", "FB + Video")),
          palette = c("red", "orange", "green", "purple")
)
```

Machine Learning in Survival Analysis.

```{r}
packages.mlr3 <- c("mlr3proba", "mlr3learners")
install.packages(packages.mlr3)
lapply(X = packages.mlr3, FUN = library, character.only = TRUE)
```

```{r}
runModel <- function (learner, task, measures, train_set, test_set, verbose = FALSE) {
  # train
  if(verbose)
    print("1. train")

  # checking lengths of train and test sets
  if(verbose) {
    cat("train_set size: ", length(x = train_set))
    cat("test_set size: ", length(x = test_set))
  }
  
  learner$train(task = task, row_ids = train_set)
  learner$model

  # predict
  if(verbose)
    print("2. predict")
  
  prediction <- learner$predict(task, row_ids = test_set)
  prediction$data$distr
  
  # evaluate
  if(verbose)
    print("3. evaluate")
  
  scores <- prediction$score(measures = measures)
  
  list(
    train_set = train_set,
    test_set = test_set,
    prediction = prediction,
    scores = scores
  )
}
```

Default variables for ML models.

```{r}
kickstarter.data.reduced <- dplyr::bind_cols(kickstarter.data %>% dplyr::select(c(1:2)), kickstarter.data %>% dplyr::select(facebook_connected, has_video))
kickstarter.data.reduced

# create task
task.kickstarter <- mlr3proba::TaskSurv$new(
  id = "kickstarter", 
  backend = kickstarter.data.reduced, 
  time = "day_succ", 
  event = "Status", 
  type = "right"
)

# select metrics for measuring performance
measures <- lapply(c("surv.cindex", "surv.graf"), mlr3::msr)

# train test split
train_set <- sample(x = task.kickstarter$nrow, size = 0.8 * task.kickstarter$nrow)
test_set <- setdiff(x = seq_len(length.out = task.kickstarter$nrow), y = train_set)
```

Conventional models.

Kaplan-Meier

```{r}
learner.surv.kaplan <- mlr3proba::LearnerSurvKaplan$new()
learner.surv.kaplan.results <- runModel(
  learner = learner.surv.kaplan,
  task = task.kickstarter,
  measures = measures,
  train_set = train_set,
  test_set = test_set
)
learner.surv.kaplan.results
```

Cox PH

```{r}
learner.surv.coxph <- mlr3proba::LearnerSurvCoxPH$new()

kickstarter.data.custom <- dplyr::bind_cols(
  kickstarter.data[, c(1:2)], 
  
  kickstarter.data.reduced %>% 
  dplyr::select_if(.predicate = function(x) {
  if(is.factor(x = x))
    if(length(x = levels(x = x)) >= 2)
      TRUE
    else
      FALSE
  else
    FALSE
  })
)

task.kickstarter.custom <- mlr3proba::TaskSurv$new(
  id = "custom",
  backend = kickstarter.data.custom,
  time = "day_succ",
  event = "Status",
  type = "right"
)  

learner.surv.coxph.results <- runModel(
  learner = learner.surv.coxph, 
  task = task.kickstarter.custom, 
  measures = measures, 
  train_set = train_set, 
  test_set = test_set
)

learner.surv.coxph.results
```

Installing more dependencies for mlr3 models.

```{r}
remotes::install_github("mlr-org/mlr3extralearners")
library(mlr3extralearners)

packages.mlr3.dependencies <- c("survivalmodels", "partykit", "coin", "randomForestSRC", "pracma", "xgboost", "survivalsvm")
install.packages(packages.mlr3.dependencies)
lapply(X = packages.mlr3.dependencies, FUN = library, character.only = TRUE)
```

Installing dependencies to run Python.

```{r}
install.packages("reticulate")
library(reticulate)
reticulate::use_python(python = "D:/Program Files/Python39/python.exe")
```

ML models.

Regression tree.

```{r}
learner.surv.rpart <- mlr3proba::LearnerSurvRpart$new()
learner.surv.rpart.results <- runModel(
  learner = learner.surv.rpart,
  task = task.kickstarter,
  measures = measures,
  train_set = train_set,
  test_set = test_set
)
learner.surv.rpart.results
```

Conditional inference tree.

```{r}
learner.surv.ctree <- mlr3extralearners::LearnerSurvCTree$new()
learner.surv.ctree.results <- runModel(
  learner = learner.surv.ctree,
  task = task.kickstarter,
  train_set = train_set,
  test_set = test_set
)
learner.surv.ctree.results
```

XGBoost.

```{r}
learner.surv.xgboost <- mlr3learners::LearnerSurvXgboost$new()

kickstarter.data.custom <- kickstarter.data.reduced %>% dplyr::mutate_if(.predicate = is.factor, .funs = as.integer)

task.kickstarter.custom <- mlr3proba::TaskSurv$new(
  id = "custom",
  backend = kickstarter.data.custom,
  time = "day_succ",
  event = "Status",
  type = "right"
)  

learner.surv.xgboost.results <- runModel(
  learner = learner.surv.ctree,
  task = task.kickstarter.custom,
  measures = measures,
  train_set = train_set,
  test_set = test_set
)

learner.surv.xgboost.results
```

Akritas KNN.

```{r}
learner.surv.akritas <- mlr3extralearners::LearnerSurvAkritas$new()

kickstarter.data.custom <- dplyr::bind_cols(
  kickstarter.data[, c(1:2)], 
  
  kickstarter.data.reduced %>% 
  dplyr::select_if(.predicate = function(x) {
  if(is.factor(x = x))
    if(length(x = levels(x = x)) >= 2)
      TRUE
    else
      FALSE
  else
    FALSE
  })
)

task.kickstarter.custom <- mlr3proba::TaskSurv$new(
  id = "custom",
  backend = kickstarter.data.custom,
  time = "day_succ",
  event = "Status",
  type = "right"
)

learner.surv.akritas.results <- runModel(
  learner = learner.surv.akritas, 
  task = task.kickstarter.custom, 
  measures = measures, 
  train_set = train_set, 
  test_set = test_set
)

learner.surv.akritas.results
```

Survival random forest

```{python}

```

SVM.

```{r}
install.packages("quadprog")
library(quadprog)
```

```{r}
learner.surv.svm <- mlr3extralearners::LearnerSurvSVM$new()
learner.surv.svm$param_set$values = mlr3misc::insert_named(x = learner.surv.svm$param_set$values, y = list(gamma.mu = 1.0))
learner.surv.svm.results <- runModel(
  learner = learner.surv.svm, 
  task = task.kickstarter, 
  measures = measures, 
  train_set = train_set[1:100], 
  test_set = test_set,
  verbose = T
)

learner.surv.svm.results
```
